Untitled

### 2017-02-03 Manuscript/Manuscript using actual data.Rmd
changes to shiny app

>>>>

**eFigure 1: Difference in life expectancy between black in white males, United States, 1969-2013**

![Difference in life expectancy between black in white males, United States, 1969-2013.](/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Manuscript/export.graph.Men.bmp)

**eFigure 2: Difference in life expectancy between black in white females, United States, 1969-2013**

![Difference in life expectancy between black in white females, United States, 1969-2013.](/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Manuscript/export.graph.Women.bmp)
